gratia: An R package for exploring generalized additive models

### 2025-08-07 README.Rmd
spell check

The English word "grace" derives from the Latin *gratia*, meaning "favor, charm,
thanks" ([according to Merriam Webster](https://www.merriam-webster.com/dictionary/grace)).

The chair that Grace Wabha currently holds is named after 
[Isaac J Schoenberg](https://en.wikipedia.org/wiki/Isaac_Jacob_Schoenberg), a
former University Madison-Wisconsin Professor of Mathematics, who in a 1946
paper provided the first mathematical reference to "splines". (Hence the
previous name for the package.)

>>>>

The English word "grace" derives from the Latin *gratia*, meaning "favour, charm,
thanks" ([according to Merriam Webster](https://www.merriam-webster.com/dictionary/grace)).

The chair that Grace Wahba currently holds is named after 
[Isaac J Schoenberg](https://en.wikipedia.org/wiki/Isaac_Jacob_Schoenberg), a
former University Madison-Wisconsin Professor of Mathematics, who in a 1946
paper provided the first mathematical reference to "splines". (Hence the
previous name for the package.)
